### 2024-02-14 parts/starfree.tex
typo

In the spirit of previous characterizations of subclasses of $\ZPoly$ in terms
of \emph{polynomial pumping arguments}
\cite{doueneau2021pebble,doueneau2022hiding,LOPEZ23b}, we will provide a
semantic property in the form of \cref{k-combinatorial:def}, that is conjecture
to characterize $\NPoly$ inside $\ZPoly$, even in the non-commutative setting.

>>>>

In the spirit of previous characterizations of subclasses of $\ZPoly$ in terms
of \emph{polynomial pumping arguments}
\cite{doueneau2021pebble,doueneau2022hiding,LOPEZ23b}, we will provide a
semantic property in the form of \cref{k-combinatorial:def}, that is conjectured
to characterize $\NPoly$ inside $\ZPoly$, even in the non-commutative setting.
